\textit{Supplementary materials for: } High-level cognition during story listening is reflected in high-order dynamic correlations in neural activity patterns

### 2021-05-31 paper/supplementary_materials.tex
WIP supplemental update

>>>>

\begin{figure}[p!]
\centering
\includegraphics[width=0.95\textwidth]{figs/sim_heatmaps_time}
  \caption{\textbf{Recovery heatmap of simulated first-order and
      second-order dynamic correlations across time and widths.}  Each panel displays a
    heatmap of the average correlations
    between the vectorized upper triangles of the recovered
    first-order and second-order correlation matrices and the true
    (simulated) first-order and second order correlation matrices
    across varying times for each synthetic dataset and averaged
    over all features amounts.  (The averages are taken
    across 10 different recoveries from
    randomly generated synthetic datasets of the given category).  For a complete description of each synthetic dataset,
    see \textit{Synthetic data: simulating dynamic higher-order
      correlations}.  Estimates were computed using a Laplace kernel with widths.  \textbf{ Constant correlations.}  These datasets
    have stable (unchanging) underlying second-order correlation
    matrices.  \textbf{Random correlations.} These datasets are
    generated using a new independently drawn second-order correlation
    matrix at each timepoint.  \textbf{Ramping correlations.}
    These datasets are generated by smoothly varying the underlying
    second-order correlations between the randomly drawn correlation
    matrices at the first and last timepoints.  \textbf{Event-based
      correlations.}  These datasets are each generated using five
    randomly drawn second-order correlation matrices that each remain
    stable for a fifth of the total timecourse. try it}
\label{fig:supp_sim_heatmaps_time}
\end{figure}

\begin{figure}[p!]
\centering
\includegraphics[width=0.95\textwidth]{figs/sim_heatmaps_features}
  \caption{\textbf{Recovery heatmap of simulated first-order and
      second-order dynamic correlations across features and widths.}  Each panel displays a
    heatmap of the average correlations
    between the vectorized upper triangles of the recovered
    first-order and second-order correlation matrices and the true
    (simulated) first-order and second order correlation matrices
    across varying number of features for each synthetic dataset and averaged
    over all features amounts.  (The averages are taken
    across 10 different recoveries from
    randomly generated synthetic datasets of the given category).  For a complete description of each synthetic dataset,
    see \textit{Synthetic data: simulating dynamic higher-order
      correlations}.  Estimates were computed using a Laplace kernel with widths.  \textbf{ Constant correlations.}  These datasets
    have stable (unchanging) underlying second-order correlation
    matrices.  \textbf{Random correlations.} These datasets are
    generated using a new independently drawn second-order correlation
    matrix at each timepoint.  \textbf{Ramping correlations.}
    These datasets are generated by smoothly varying the underlying
    second-order correlations between the randomly drawn correlation
    matrices at the first and last timepoints.  \textbf{Event-based
      correlations.}  These datasets are each generated using five
    randomly drawn second-order correlation matrices that each remain
    stable for a fifth of the total timecourse. try it}
\label{fig:supp_sim_heatmaps_features}
\end{figure}
